\documentclass{article}                       
\usepackage{siunitx}                                              
\usepackage{setspace}
\usepackage{gensymb}                                              
\usepackage{xcolor}                                               
\usepackage{caption}
%\usepackage{subcaption}
\doublespacing                                                    
\singlespacing                                                    
\usepackage[none]{hyphenat}
\usepackage{amssymb}
\usepackage{relsize}
\usepackage[cmex10]{amsmath}
\usepackage{mathtools}
\usepackage{amsmath}                                              
\usepackage{commath}                                              
\usepackage{amsthm}
\interdisplaylinepenalty=2500
%\savesymbol{iint}
\usepackage{txfonts}                                              
%\restoresymbol{TXF}{iint}                                        
\usepackage{wasysym}                                              
\usepackage{amsthm}
\usepackage{mathrsfs}                                             
\usepackage{txfonts}                                              
\let\vec\mathbf{}
\usepackage{stfloats}
\usepackage{float}
\usepackage{cite}
\usepackage{cases}                                                
\usepackage{subfig}                                               
%\usepackage{xtab}
\usepackage{longtable}
\usepackage{multirow}
%\usepackage{algorithm}
\usepackage{amssymb}
%\usepackage{algpseudocode}
\usepackage{enumitem}
\usepackage{mathtools}
%\usepackage{eenrc}
%\usepackage[framemethod=tikz]{mdframed}                          
\usepackage{listings}                                             
%\usepackage{listings}
\usepackage[latin1]{inputenc}
%%\usepackage{color}{
%%\usepackage{lscape}
\usepackage{tfrupee}
\usepackage{titling}
\usepackage{hyperref}
%\usepackage{fulbigskip}
\usepackage{tikz}
\usepackage{graphicx}                                             
\lstset{
  frame=single,
  breaklines=true
}
\let\vec\mathbf{}
\usepackage{enumitem}                                             
\usepackage{graphicx}                                             
\usepackage{siunitx}
\let\vec\mathbf{}                                                 
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{tfrupee}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mwe} % for blindtext and example-image-a in example
\usepackage{wrapfig}
\begin{document}
\begin{enumerate}

	\item Find the value of $k$ for which the roots of  the quadratic equation $(k-5)x^2+2(k-5)x+2$=$0$ are equal.
	\item Find the value of $y$ for which the  distance between the points $(2,-3)$ and $(10,y)$ is $10$ units.
\item Write whether the rational number $\frac{13}{3125}$ has a decimal expansion which is  terminating or non-terminating repeating.
\item Write the $m^{th}$ term of the A.P.$\frac{1}{k}$,$\frac{1+k}{k}$,$\frac{1+2k}{k}$,........
\item if $\sin\theta+\cos\theta$=$\sqrt{2}\cos($90\degree{}$-\theta)$,find the value of $\cot\theta$.
\item $DE$ is drawn parallel to the base $BC$ of a $\triangle ABC$,meeting $AB$ at $D$ and $AC$ at $E$. if $\frac{AB}{BD}=4$ and $CE=2$cm,find $AE$.
\item A bag contains $5$ red balls and some blue balls. if the proability of drawing a blue balls. if the probability of drawing a blue ball from the bag is three times that of a red ball,find the number of blue balls in the bag.
\item The $5^ {th}$ and $15^ {th}$ terms of an A.P. are $13$ and $-17$ respectively.Find the sum of first $21$ terms of the A.P.
\item Using Euclid's Division Algorithm,find the HCF of $255$ and $867$.
\item if the point $(0,2)$ is equidistant from the points $(3,k)$ and $(k,5)$,find the value of $k$.
\item Find the value of  $'a'$ for which the pair of linear equations $2x+3y$=$7$ and $4x+ay$=$14$ has infinitely many solutions.
\item A card  is drawn at random from a well shuffled pack of $52$ playing  cards.Find the probability of getting(i) a red king (ii) a queen or a jack.
\item Show that any  positive odd integer is of the form $4q+1$ or $4q+3$ for some integer $q$
\item The ten's digit of a number is twice its unit's digit obtained by interchanging the digit is $36$ less than the original number.Find the original number.
\item The line segmet joining the points $A(2,1)$ and $B(5,-8)$ is triseected at the points $P$ and $Q$,where $P$ lies on the line $2x-y+k=0$,find the value of $K$.
\item The x-coordinate of a point $P$ is twice its y-coordinate. if $P$ is equidistant from the points $Q(2,-5)$ and $R(-3,6)$,find the coordinates of $P$.
\item show that $1,\frac{1}{2}$ and $-2$ are zeros of the polynomial  $2x^{3}+x^[2]-5x+2$.
\item Prove that  the angle between the two tangents drawn from an external point to a circle is supplimentary to  the angle subtended by the line-segment  joining the points of contact at the centre.
\item $S$ and $T$ are points on the siddes $PR$ and $QR$ of  $\triangle PQR$ such that $\angle P$=$\angle RTS$.Show that $\triangle RPQ$ $\sim\triangle RTS$.
\item In an equilateral $\triangle ABC$,$D$ is a point on the side $BC$ such that $BD$=$\frac{1}{3}BC$
.Prove that $9AD^2$=$7AB^2$.
\item Prove that : $\frac{1}{\csc\theta+\cot\theta}-\frac{1}{\sin\theta}$=$\frac{1}{\sin\theta}-\frac{1}{\csc\theta-\cot\theta}$
\item If $\tan\theta$+$\sin\theta=m$,$\tan\theta-\sin\theta=n$,show that $m^2-n^2$=$4\sqrt{mn}$
\item A chord of a circle,of radius $15$cm,subtends an angle of $60\degree{}$ at the centre of the circle.Find the area of major and minor segments(Take  $\pi$=$3.14$,$\sqrt{3}$=$1.73$)
\item A sphere of diameter $12$cm is dropped in a right circular cylindrical vessel,partly filled with water.If the sphere is completely submerged in ater,the water level in the vessel rises by $3\frac{3}{9}$cm.Find the diameter of the cylindrical vessel.
\item A cylinder whose height is two-third of its diameter, has the same volme as that of a sphere of radius $4$cm.Find the radius of base of the cylinder.
\item The following table gives the daily income of $50$ labourers: \\
	\begin{tabular}{|c|c|c|c|c|c|}             \hline                                                    \textbf{Daily Income (\rupee)} & $100-120$ & $120-140$ & $140-160$ & $160-180$ &  $180-200$ \\                                                    \hline                                                    \textbf{Number of Labourers} & $12$ & $14$ & $8$ & $6$ & $10$ \\
\hline
	\end{tabular} \\

Find the mean and mode of the above data.
\item Two taps together can fill a tank in $6$ hours.The tap of larger diameter takes $9$hours less than the smaller one to fill the tank seperately.Find the time in which each  tap can fill the tank seperately.
\item Solve for $x$: $\frac{x+1}{x-1}-\frac{x-1}{x+1}$=$\frac{5}{6}$,$x \neq 1,-1$
\item Prove that the ratio of the areas of two simi lar tr iangle is equal to the square of the ratio of their corresponding sides.
\item Prove that in a triangle,if the square of one side is equal to sum of the squares of the other  two sides,the angle opposition the first side is a right angle.
\item Write the steps of construction for drawing a $\triangle ABC$ in which $BC=8$cm,$\angle B=45\degree{}$ and $\angle C= 30\degree{}$.Now write the steps of connection for drawing a triangle whose sides are $\frac{3}{4}$ of the corresponding sides of $\triangle ABC$.
\item The sum of the first $n$ terms of an A.P.is $5n^2+3n$.If its $m^{th}$ terms is $168$,find the value of $m$.Also find the $20^{th}$ term of the A.P.
\item The $4^{th}$ and the last terms of an A.P. are $11$ and $89$ respectively.If there are $30$terms in the A.P.,find the A.P and its $23^ {rd}$ term.
\item Prove that : $(\frac{\sin A}{1-\cos A}-\frac{1-\cos A}{\sin A})$.$(\frac{\cos A}{1-\sin A}-\frac{1-\sin A}{\cos A})$=$4$.
\item A statue,$1.46$m tall,stands on a pedestal.From a point on the ground the angle of elevation of the top of the statue is $60\degree{}$ and from the same point angle of elevation of the top of the pedestal is $45\degree{}$.Find the height of the pedestal.(use $\sqrt{3}=1.73$)
\item Sudhakar donated $3$ cylindrical drums to store cereals to an orphanage.If radius of each drum is $0.7$m and height $2$m,find the volume of each drum.if each drum costs \rupee~$350$ per $m^3$,find the amount spent by sudhakar for orphanage.What value is exhibited in the question.(Use $\pi$ = $\frac{22}{7}$)
\item  The median of  the following data is $52.5$.if the total frequency is $100$,find the value of $x$ and $y$. \\
	\begin{tabular}{|c|c|}
\hline
		\textbf{classes} & \textbf{frequency} \\
\hline
         0-10 & 2 \\
\hline
         10-20 & 5 \\
\hline
         20-30 & x \\
\hline
        30-40 & 12 \\
\hline
        40-50 & 17 \\
\hline
        50-60 & 20 \\
\hline
         60-70 & y \\
\hline
         70-80 & 9 \\
\hline
          80-90 & 7 \\
\hline
          90-100 & 4 \\
\hline
	\end{tabular}
\end{enumerate}
\end{document}
